Quantifying the ease of viral escape from broad and narrow antibodies to influenza virus hemagglutinin

### 2017-10-05 paper/manuscript.tex
some work on abstract

\title{Contrasting the potential for viral escape from broad and narrow antibodies by complete mapping of the antigenic effects of single amino-acid mutations to influenza hemagglutinin}

@@

\begin{abstract}
Broadly neutralizing antibodies are of great interest as therapeutics to treat influenza and are the desired products of future universal influenza vaccines. 
It is important to understand viral potential for escape from antibodies and to develop ways to compare how easy or difficult it is for viral escape between various antibodies. 
We previously demonstrated a method to measure the effects of all amino-acid mutations in influenza HA on viral escape from neutralizing antibodies. 
Here we apply this technique to 'broadly neutralizing' antibodies with reactivity spanning multiple influenza subtypes, including antibodies targeting the HA receptor-binding site and stalk domain. We find quantitatively similar distributions of escape mutations to a relatively broad antibody targeting the receptor-binding site (s139) and to several narrow-specificity antibodies targeting nearby antigenic regions of the head domain (H17-L19, others?). 
In contrast to the ease of escape from head-binding antibodies of various breadths, stalk-binding antibodies can only be evaded by a paucity of mutations with relatively small effects.  
For the antibodies studied here, antibody breadth is not an indicator of difficulty for viral escape.  
Instead, targeting a mutationally intolerant epitope in the stalk region seems to limit viral escape mutations to a few relatively ineffective options
\end{abstract}

>>>>

\title{Quantifying the ease of viral escape from broad and narrow antibodies to influenza virus hemagglutinin}

@@

\begin{abstract}
Nearly all viruses exhibit some antigenic variation.
However, the extent of this variation ranges widely across viruses and antibodies.
Influenza virus exhibits high antigenic variation, and can completely escape most neutralizing antibodies with single mutations.
However, some rare antibodies neutralize many influenza virus strains.
It is unclear how easily the virus might escape such broad antibodies if there was strong selection to do so.
Here we map all single amino-acid mutations to an H1 influenza hemagglutinin that increase resistance to several broad antibodies.
Crucially, our approach both identifies antigenic mutations and quantifies their effect size.
We find mutations that increase resistance to all antibodies tested, but the effect sizes range widely. 
Single mutations completely escape a broad antibody targeting the hemagglutinin receptor-binding pocket, similar to escape from narrow strain-specific antibodies.   
In contrast, the few mutations selected by broad antibodies targeting the hemagglutinin stalk have only small effects. 
Overall, our work demonstrates a method to quantify the ease of viral antibody escape, and shows that antibody breadth is not necessarily an indicator of the difficulty of viral escape.
%Instead, targeting a mutationally intolerant epitope in the stalk region seems to limit viral escape mutations to a few relatively ineffective options
\end{abstract}
